Tropical Andes plant species BIEN data

### 2023-07-18 code/L0/L0_TropicalAndes_plants_BIEN_occ.Rmd
remove unneccessary code and update file paths

# Get data for Tropical Andes from BIEN database
```{r}
# occurrence data
#TropicalAndes_BIEN_occ <- BIEN_occurrence_box(min.lat = -94, max.lat = -54, min.long = -24, max.long = 14,species = plant_species, all.taxonomy = TRUE, political.boundaries = TRUE, observation.type = TRUE)
#line above returned 0 records
TropicalAndes_BIEN_occ <- BIEN_occurrence_country(country = country_vector, all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

@@

# Write data to csv
```{r}
TropicalAndes_BIEN_occurrence_path <- file.path(output_path,"TropicalAndes_BIEN_occ.csv") 
write.csv(TropicalAndes_BIEN_occ, file = TropicalAndes_BIEN_occurrence_path)

TropicalAndes_BIEN_species_list_path <- file.path(output_path, "TropicalAndes_BIEN_species_list.csv")
write.csv(TropicalAndes_BIEN_species_list, file = TropicalAndes_BIEN_species_list_path)
```

>>>>

# Get occurrence data for Tropical Andes from BIEN database
```{r}
TropicalAndes_BIEN_occ <- BIEN_occurrence_country(country = country_vector, all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

@@

# Write data to csv
```{r}
TropicalAndes_BIEN_occurrence_path <- file.path(output_path,"TropicalAndes_BIEN_plant_occ.csv") 
write.csv(TropicalAndes_BIEN_occ, file = TropicalAndes_BIEN_occurrence_path)

TropicalAndes_BIEN_species_list_path <- file.path(output_path, "TropicalAndes_BIEN_plant_species_list.csv")
write.csv(TropicalAndes_BIEN_species_list, file = TropicalAndes_BIEN_species_list_path)
```
